Pulling oral and IV data from CvTdb

### 2024-01-25 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Fixing dose_level_units_original to account for name change in CvTdb table.

```{r SQL_queries}
# Need to make this in a specified ordered
# First all IDs (so I can check them quickly)
# Note that this uses an ALIAS for each table which is later specified in
# the FROM and LEFT JOIN statments
query <- paste0(
  "SELECT distinct ",
  "a.id, a.time_original,  a.time_hr, a.conc_original, a.conc_sd_original, a.conc, a.conc_sd, ",
  "b.id, b.analyte_name_original, b.analyte_dtxsid, b.analyte_casrn, ",
  "b.fk_analyzed_chemical_id, b.fk_test_chemical_id, ",
  "b.test_substance_dtxsid, b.analyte_name_secondary_original, ",
  "b.conc_medium_normalized, b.time_units_original, b.conc_units_original, ",
  "b.loq, b.loq_units, b.n_subjects_in_series, b.radiolabeled, ",
  "c.id, c.administration_route_normalized, c.fk_dosed_chemical_id, c.dose_volume, c.dose_vehicle, ",
  "c.dose_duration, c.dose_duration_units, c.dose_frequency, c.fasting_period, ",
  "c.dose_level_normalized, c.dose_level_original, c.dose_level_original_units, ",
  "d.id, d.weight_kg, d.species, d.sex, d.age, d.age_units, d.age_category, ",
  "e.id, e.pmid, e.year, e.other_study_identifier, e.url, e.doi, e.extracted ",

@@

```{r}
cvt_date <- Sys.Date()
cvt <- cvt_df
save(cvt, file = "data/cvt.rda", compress = "bzip2")
save(cvt_date, file = "data/cvt_date.rda")
```

>>>>

```{r SQL_queries}
# Need to make this in a specified ordered
# First all IDs (so I can check them quickly)
# Note that this uses an ALIAS for each table which is later specified in
# the FROM and LEFT JOIN statments
query <- paste0(
  "SELECT distinct ",
  "a.id, a.time_original,  a.time_hr, a.conc_original, a.conc_sd_original, a.conc, a.conc_sd, ",
  "b.id, b.analyte_name_original, b.analyte_dtxsid, b.analyte_casrn, ",
  "b.fk_analyzed_chemical_id, b.fk_test_chemical_id, ",
  "b.test_substance_dtxsid, b.analyte_name_secondary_original, ",
  "b.conc_medium_normalized, b.time_units_original, b.conc_units_original, ",
  "b.loq, b.loq_units, b.n_subjects_in_series, b.radiolabeled, ",
  "c.id, c.administration_route_normalized, c.fk_dosed_chemical_id, c.dose_volume, c.dose_vehicle, ",
  "c.dose_duration, c.dose_duration_units, c.dose_frequency, c.fasting_period, ",
  "c.dose_level_normalized, c.dose_level_original, c.dose_level_units_original, ",
  "d.id, d.weight_kg, d.species, d.sex, d.age, d.age_units, d.age_category, ",
  "e.id, e.pmid, e.year, e.other_study_identifier, e.url, e.doi, e.extracted ",

@@

```{r}
cvt_date <- Sys.Date()
cvt <- cvt_df
cvt <- cvt %>% mutate(conc_normalized_units = "mg/L")
save(cvt, file = "data/cvt.rda", compress = "bzip2")
save(cvt_date, file = "data/cvt_date.rda")
```
